---
output: pdf_document
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\doublespacing

# Appendix A: R Code for Chapter 5 {-}

\singlespace

Required: R Packages from CRAN

\small
```{r, echo=TRUE, eval=FALSE}
if (!require(tidyverse)){
  install.packages("tidyverse")
  library(tidyverse)
}
if (!require(furniture)){
  install.packages("furniture")
  library(furniture)
}
if (!require(here)){
  install.packages("here")
  library(here)
}
if (!require(devtools)){
  install.packages("devtools")
  library(devtools)
}
```
\normalsize

Required: R Packages from GitHub

\small
```{r, echo=TRUE, eval=FALSE}
if (!require(MarginalMediation)){
  devtools::install_github("tysonstanley/MarginalMediation")
  library(MarginalMediation)
}
```
\normalsize

\clearpage

## Examples from Chapter 5 {-}

Figure \ref{fig:interaction} on page \pageref{fig:interaction}

\small
```{r interaction_example, eval=FALSE}
```
\normalsize

\clearpage


## Monte Carlo Simulation {-}

Notably, the code for both the binary mediator condition and the count mediator condition we run via the Terminal as, once the directory was where the R file was located:

\small
```{bash, eval=FALSE}
Rscript Analyses_MMMC_scriptBinary.R 'c(1:45)'
```
\normalsize

\noindent and

\small
```{bash, eval=FALSE}
Rscript Analyses_MMMC_scriptCount.R 'c(1:45)'
```
\normalsize

Binary Mediator

\small
```{r, eval=FALSE}
## Marginal Mediation: Monte Carlo Simulation Study
##   BINARY Mediator
## Tyson S. Barrett
##
## devtools::install_github("tysonstanley/MarginalMediation")

args <- commandArgs(TRUE)
args <- eval(parse(text = args))
library(MarginalMediation)
library(tidyverse)

## Create all combinations of independent variables
cond_binary <- expand.grid(
  samplesize = c(50, 100, 200, 500, 1000),
  effecta = c(.55, 1.45, 2.22),
  effectb = c(.24, .62, 1.068),
  effectc = c(.3)
)

## Population Models
## Binary Mediator
data_genB <- function(ps, reps, samplesize, effecta, effectb, effectc) {
  set.seed(84322)
  Xc <- rnorm(ps)
  z <- effecta * Xc + rnorm(ps, 0, 1)
  pr <- 1 / (1 + exp(-z))
  M <- rbinom(ps, 1, pr)
  Y <- effectb * M + effectc * Xc + rnorm(ps, 0, 1)
  M <- factor(M)
  df <- data.frame(Y, M, Xc)
  bin <- vector("list", reps)

  print(cbind(samplesize, effecta, effectb))
  print(lm(Y ~ M + Xc)$coefficients)
  print(lm(scale(Y) ~ M + Xc)$coefficients)
  med <- amed(glm(M ~ Xc, df, family = "binomial"))

  for (i in 1:reps) {
    d <- df[sample(ps, samplesize), ]
    pathbc <- glm(Y ~ M + Xc, data = d)
    patha <- glm(M ~ Xc, data = d, family = "binomial")
    bin[[i]] <- mma(pathbc, patha,
      ind_effects = c("Xc-M"),
      boot = 500
    )
    bin[[i]] <- list(
      "IndEffects" = bin[[i]]$ind_effects,
      "DirEffects" = bin[[i]]$dir_effects,
      "Boot" = bin[[i]]$boot,
      "Total" = lm(Y ~ Xc, d)$coefficients,
      "MedSize" = med
    )
    cat("\r", i)
  }
  print(exp(glm(M ~ Xc, family = "binomial")$coefficients))
  return(bin)
}

i = 0
for (j in args){
  set.seed(84322)
  i = i + 1
  cat("\nNumber:", j, "\n\n")
  
  out = data_genB(1e6, 500, 
                  cond_binary[args[[i]],1], 
                  cond_binary[args[[i]],2], 
                  cond_binary[args[[i]],3], 
                  cond_binary[args[[i]],4])
  
  save(out, file = paste0("Sims_Data/Binary2_", 
                          cond_binary[args[[i]],1], "_",
                          cond_binary[args[[i]],2], "_",
                          cond_binary[args[[i]],3], "_",
                          cond_binary[args[[i]],4], ".rda"))
  
  cat("\nNumber:", j, "\n\n")
  cat("\nConditions Complete:\n",
      " Sample size =", cond_binary[args[[i]],1], 
      "\n  A path      =", cond_binary[args[[i]],2], 
      "\n  B path      =", cond_binary[args[[i]],3], 
      "\n  C path      =", cond_binary[args[[i]],4], "\n")
}
```
\normalsize

Count Mediator

\small
```{r, eval=FALSE}
## Marginal Mediation: Monte Carlo Simulation Study
##   COUNT Mediator
## Tyson S. Barrett
##
## devtools::install_github("tysonstanley/MarginalMediation")

args <- commandArgs(TRUE)
args <- eval(parse(text = args))
library(MarginalMediation)
library(tidyverse)

## Create all combinations of independent variables
cond_count = expand.grid(
  samplesize = c(50, 100, 200, 500, 1000),
  effecta    = c(.3, .6, 1.1),
  effectb    = c(.084, .265, .49),
  effectc    = c(0, .3)
)

## Population Models
## Count Mediator
data_genC = function(ps, reps, samplesize, effecta, effectb, effectc){
  set.seed(84322)
  Xc = rnorm(ps)
  m1 = exp(effecta * Xc)
  M  = rpois(ps, lambda=m1)
  Y  = effectb*M + effectc*Xc + rnorm(ps, 0, 1)
  df = data.frame(Y, M, Xc)
  poi  = vector("list", reps)
  
  print(cbind(samplesize, effecta, effectb))
  print(lm(Y ~ M + Xc)$coefficients)
  print(lm(scale(Y) ~ M + Xc)$coefficients)
  med = amed(glm(M ~ Xc, df, family = "poisson"))
  
  for (i in 1:reps){
    d = df[sample(ps, samplesize), ]
    pathbc = glm(Y ~ M + Xc, data = d)
    patha  = glm(M ~ Xc, data = d, family = "poisson")
    poi[[i]] = mma(pathbc, patha,
                   ind_effects = c("Xc-M"),
                   boot = 500)
    poi[[i]] = list("IndEffects" = poi[[i]]$ind_effects, 
                    "DirEffects" = poi[[i]]$dir_effects, 
                    "Boot"       = poi[[i]]$boot, 
                    "Total"      = lm(Y ~ Xc, d)$coefficients,
                    "MedSize"    = med)
    cat("\r", i)
  }
  print(exp(glm(M ~ Xc, family = "poisson")$coefficients))
  return(poi)
}

i = 0
for (j in args){
  set.seed(84322)
  i = i + 1
  cat("\nNumber:", j, "\n\n")
  
  out = data_genC(1e6, 500, 
                  cond_count[args[[i]],1], 
                  cond_count[args[[i]],2], 
                  cond_count[args[[i]],3], 
                  cond_count[args[[i]],4])
  
  save(out, file = paste0("Sims_Data/Count2_", 
                          cond_count[args[[i]],1], "_",
                          cond_count[args[[i]],2], "_",
                          cond_count[args[[i]],3], "_",
                          cond_count[args[[i]],4], ".rda"))
  
  cat("\nNumber:", j, "\n\n")
  cat("\nConditions Complete:\n",
      " Sample size =", cond_count[args[[i]],1], 
      "\n  A path      =", cond_count[args[[i]],2], 
      "\n  B path      =", cond_count[args[[i]],3], 
      "\n  C path      =", cond_count[args[[i]],4], "\n")
}
```
\normalsize

\clearpage

## Monte Carlo Simulation Data Analyses {-}

Data Preparations for tables and figures around page \pageref{tab_discrep}

\small
```{r sim_data_clean, eval=FALSE}
```
\normalsize

Table \ref{tab_discrep} on page \pageref{tab_discrep}

\small
```{r sim_total_tab, eval=FALSE}
```
\normalsize

Figure \ref{fig:totaltotal} on page \pageref{fig:totaltotal}

\small
```{r total_fig, eval=FALSE}
```
\normalsize

Figures \ref{fig_power}, \ref{fig_acc}, and \ref{fig_ci} on pages \pageref{fig_power}, \pageref{fig_acc}, and \pageref{fig_ci}, respectively.

\small
```{r acc_power_cover, eval=FALSE}
```
\normalsize

